What's in a Name? Linear Temporal Logic Literally Represents Time Lines

### 2022-12-30 paper/main.tex
some things
add one more example

    \author[inst1]{Marijn Heule\corref{cor2}}
    \ead{marijn@cmu.edu}

@@

\begin{example}
    In \cref{fig:ex2}, one can reason about two timelines: the upper timeline starts with $p$ at the first time step, followed by entering the grey box with one step of $!p$ and one step of $p$. Then at the end of the grey box, we reenter the box, with the next time step being $!p$, and so on. The lower timeline starts with one step of $!p$ and one step of $p$ outside the grey box, and then enter the infinite run of $!p$ and $p$ repeating.
    \begin{figure}[!h]
        \centering
        \includegraphics[scale=0.4]{examples/ex2/ex2.png}
        \caption{Example timeline for specification ``$p$ oscillates every time step''}
        \label{fig:ex2}
    \end{figure}
\end{example}

@@

\begin{example}
    Zhao and Rozier~\cite{ZR14} presents a model verification specification says ``[i]f a TSAFE command is sent to an aircraft, controller/AutoResolver should then hand off the control of this aircraft'' which corresponds to \ltl\ formula
    \[
        \always (\texttt{tsafe.TSAFE\_command1} \land \texttt{controller.CTR\_control\_1} \limplies \nextt (\neg \texttt{controller.CTR\_control\_1}))
    \]
    For simplicity, we swap the concrete atomic proposition to $a, b, c$ and get
    \[
        \always (a \land b \limplies \nextt (\neg b))
    \]
    For this \ltl\ formula, our tool generates the timeline representation in \cref{fig:ex14}.
    \begin{figure}[h!]
        \centering
        \includegraphics[scale=0.3]{examples/ex14/ex14.png}
        \caption{Timeline for $\always (a \land b \limplies \nextt (\neg b))$}
        \label{fig:ex14}
    \end{figure}
\end{example}

>>>>

    \author[inst1]{Marijn~J.H.~Heule\corref{cor2}}
    \ead{marijn@cmu.edu}

@@

\begin{example}
    In \cref{fig:ex2}, one can reason about two parallel timelines: the upper timeline starts with $p$ at the first time step, followed by entering the grey box with one step of $!p$ and one step of $p$. Then at the end of the grey box, we reenter the box, with the next time step being $!p$, and so on. The lower timeline starts with one step of $!p$ and one step of $p$ outside the grey box, and then enter the infinite run of $!p$ and $p$ repeating.
    \begin{figure}[!h]
        \centering
        \includegraphics[scale=0.4]{examples/ex2/ex2.png}
        \caption{Example timeline for specification ``$p$ oscillates every time step''}
        \label{fig:ex2}
    \end{figure}
\end{example}

\begin{example}
    In \cref{fig:ex15}, one can reason about one timeline: the atomic proposition $a$ is false for finitely many time steps as signified by two nodes with $!a$ separated by $\cdots$ (could also be zero time step); followed by one node with $a$ which substantiates the specification of ``$a$ eventually true''; once $a$ is true at some point, the later time steps can behave arbitrarily as signified by the infinite run of $1$ (true) in the grey box.
    \begin{figure}[!h]
        \centering
        \includegraphics[scale=0.4]{examples/ex15/ex15.gv.png}
        \caption{Example timeline for specification ``$a$ is eventually true''}
        \label{fig:ex15}
    \end{figure}
\end{example}

@@

\begin{example}
    Zhao and Rozier~\cite{ZR14} presents a model verification specification says ``[i]f a TSAFE command is sent to an aircraft, controller/AutoResolver should then hand off the control of this aircraft'' which corresponds to \ltl\ formula
    \[
        \always (\texttt{tsafe.TSAFE\_command1} \land \texttt{controller.CTR\_control\_1} \limplies \nextt (\neg \texttt{controller.CTR\_control\_1}))
    \]
    For simplicity, we swap the concrete atomic proposition to $a,b$ and get
    \[
        \always (a \land b \limplies \nextt (\neg b))
    \]
    For this \ltl\ formula, our tool generates the timeline representation in \cref{fig:ex14}.
    \begin{figure}[h!]
        \centering
        \includegraphics[scale=0.3]{examples/ex14/ex14.png}
        \caption{Timeline for $\always (a \land b \limplies \nextt (\neg b))$}
        \label{fig:ex14}
    \end{figure}
\end{example}
